Supplementary Material

### 2022-03-08 supplement/supplement.Rmd
CD revision 2, minor changes and updates

```{r sifig13, fig.height=7.5, fig.width=5.25, fig.cap="Interaction plots, p-curves, effect size curves, sample sizes, and specification grids for task version by violence and task version by poverty"}
vio_ses_updating
```

>>>>

```{r sifig13, fig.height=7.5, fig.width=5.25, fig.cap="Interaction plots, p-curves, effect size curves, sample sizes, and specification grids for task version by violence and task version by poverty. Teal lines and points reflect individual multiverse effect sizes with p-values < .05."}
vio_ses_updating
```
